A generalized definition of multidimensional item response theory parameters

### 2022-11-10 output/paper_draft/paper_M2PLM_parameters.Rmd
Drops the use of `TRAIT_MODULE` (substituted by `TRAIT_NORM`)

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_MODULE`$.

@@

The root we are interested in is found for $`r IRF_MAX_SLOPE_EQ`$
(the other ones occur when $`r IRF_ABBR`$ equals 0 and 1,
which result in improper values of $`r TRAIT_MODULE`$).
The slope in direction $`r DIR_ANGLE_VEC`$ is given by

>>>>

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_NORM`$.

@@

The root we are interested in is found for $`r IRF_MAX_SLOPE_EQ`$
(the other ones occur when $`r IRF_ABBR`$ equals 0 and 1,
which result in improper values of $`r TRAIT_NORM`$).
The slope in direction $`r DIR_ANGLE_VEC`$ is given by
